Efficiently Handling Guards in the Low Level Design of RPython's Tracing JIT

### 2012-08-10 talk/vmil2012/paper.tex
add another todo
start explaining the example

\todo{explain example}
%___________________________________________________________________________

\begin{figure}
    \input{figures/example.tex}
    \caption{Example Program}
    \label{fig:trace-log}
\end{figure}

@@

\section*{Acknowledgements}
\section*{Appendix}
\begin{figure*}
    \include{figures/ops_count_table}
    \caption{Relative numbers of operations in the traces generated for
    different benchmarks}
    \label{fig:ops_count}
\end{figure*}
\begin{figure*}
\centering
\includegraphics[width=\textwidth]{figures/ops_pie.pdf}
\caption{Relative frequency of operations before and after optimization}
\label{fig:ops_pie}
\end{figure*}
\bibliographystyle{abbrv}
\bibliography{zotero,paper}
\listoftodos
\end{document}

>>>>

\begin{figure}
    \input{figures/example.tex}
    \caption{Example Program}
    \label{fig:example}
\end{figure}

Figure~\ref{fig:example} shows an example RPython function that checks
whether a number reduces to 1 with less than 100 steps of the Collatz process.
It uses an \lstinline{Even} and an \lstinline{Odd} class to box the numbers, to
make the example more interesting. If the loop in \lstinline{check_reduces} is
traced when \lstinline{a} is a multiple of four, the unoptimized
trace looks like in Figure~\ref{fig:unopt-trace}. The line numbers in the trace
correspond to the line numbers in Figure~\ref{fig:trace-log}.

\begin{figure}
    \input{figures/unopt-log.tex}
    \caption{Unoptimized trace}
    \label{fig:unopt-trace}
\end{figure}

@@

\section*{Acknowledgements}
\section*{Appendix}
\todo{remove this section and the figures}
\begin{figure*}
    \include{figures/ops_count_table}
    \caption{Relative numbers of operations in the traces generated for
    different benchmarks}
    \label{fig:ops_count}
\end{figure*}
\begin{figure*}
\centering
\includegraphics[width=\textwidth]{figures/ops_pie.pdf}
\caption{Relative frequency of operations before and after optimization}
\label{fig:ops_pie}
\end{figure*}
\bibliographystyle{abbrv}
\bibliography{zotero,paper}
\listoftodos
\end{document}
